Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-18 Manuscript.Rmd
Change in figures and added AR/sliding window accessory analyses

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
output:
  pdf_document: default
  html_document: default
  word_document: 
    reference_docx: Style_reference.docx
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

Next, we identified areas that were solely related to either literature. We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al. [-@Yeo2011]. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI. This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.

@@

In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) [@Hubert1985] as the reference metric of agreement between two clusterings. The adjusted rand index estimates the rate at which every pair of nodes in partition A were equally assigned to the same/different parcels on partition B, over all possible changes (e.g. clustered together on A, but separately on B). The resulting ratio is compared to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions. Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme. *(SHOULD WE INCLUDE THIS? The mutual information results would probably need to go in the supplemental materials) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions. While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case. Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).*

@@

Before determining the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004]. Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model. Since modularity is agnostic to the desired number of clusters, it was capable of finding more than two communities in our datset. Thus, if both methods agreed in the number and topological organization of the current communities, it would add confidence to our results. We quantified the cross-method agreement with the adjusted rand index (ARI). ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g. clustered together in partition 1, but separately in 2), and has the benefit of being agnostic to labeling schemes [@Hubert1985]. Figure 3 shows the distribution of ARI values across subjects. **It is worth noting that the adjusted rand index has well known limitations (Fortunato & Hric, 2016). To compensate for this, we also performed all the upcoming analyses with the variation of information index (VI). This distance measure denotes how much information is gained by adding the second partition (thus, lower values are better), and is known for its robustness. Both RI and VI analyses agreed in the results they yielded, but we only report RI due to its easier interpretability. This first plot shows the distribution of RI values between modularity and spectral partitioning for each subject.**

@@

``` {r Partition comparison: all 2 plot, fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}

# par(mfrow = c(1,2))
# corrplot(RI_all_between,
#          is.corr = F, 
#          method = "color", 
#          tl.pos = "n", 
#          tl.col = "black", 
#          cl.lim = c(0,1),
#          cl.pos = "b",
#          cl.length = 3)
# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         cl.lim = c(0,1),
         cl.length = 3,
         addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,0,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         addgrid.col = "grey90",
         mar = c(1,0,2,0), 
         add = T)
mtext(expression(bold("Subject Partitions")), line = 0.8)
mtext(expression(bold("Subject Partitions")), side = 2, line = -2.5)
mtext(expression(bold("PFC")), line = 0, at = par("usr")[1]+0.7*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.22*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Partition comparison: halves plot, fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1,1,1,1))
mtext("Subjects (Day 1 and Day 2)", line = 0)
mtext("Subjects (Day 1 and Day 2)", side = 2, line = 3)
corrplot(RI_PCC_halves, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         tl.cex = 0.1,
         cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
mtext("Subjects (Day 1 and Day 2)", line = 0)
corrplot(RI_PFC_halves, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)

@@

# plot
ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
          geom_boxplot(show.legend = F) +
          scale_fill_manual(values = Cols[seq(2)]) + 
          ylim(0, max(Halves_RIRatios_summary$RI)) +
          geom_hline(yintercept = 1) +
          labs(y = "ARI Ratio", x = "") + 
          theme_classic()
```

@@

``` {r Partition comparison: session similarity matrices plot, fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "b",
         cl.length = 3)
corrplot(RI_PCC_sess, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.length = 3)
corrplot(RI_PFC_sess, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         add = T)
```

@@

As before, we see higher agreement levels within subjects (with some exceptions). Simple permutation comparisons confirmed this intuition for the all-ROI (p = `r Sess_overallComparison[[3]]$Pval`; Cohen's D `r round(Sess_overallComparison[[4]], digits = 2)`), PCC (p = `r Sess_PCCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PCCComparison[[4]], digits = 2)`), and mPFC (p = `r Sess_PFCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PFCComparison[[4]], digits = 2)`) divisions. In order to quantify the consistency and specificity of these partitions, we again applied the RI ratio index, but this time using the mean RI among all of a subject's sessions in the denominator. The following plot shows the results for PCC and mPFC separately.

@@

ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
          geom_boxplot(show.legend = F) +
          scale_fill_manual(values = Cols[seq(2)]) + 
          ylim(0, max(Sess_RIRatios_summary$RI)) +
          geom_hline(yintercept = 1) +
          labs(y = "ARI Ratio", x = "") + 
          theme_classic()
```

@@

### *Stability per subject*

@@

@@

### temporary fix to add z coordinates (these will be computed during the initial analysis from now on)
for (i in seq(nSubj)) {
  tempIndex <- Summaries[[i]]$Vertex %in% Variance[[i]]$Vertex
  Variance[[i]]$SubjID <- rep(subjList[i], nrow(Variance[[i]]))
  Variance[[i]]$tempX <- Summaries[[i]]$x[tempIndex]
  Variance[[i]]$tempZ <- Summaries[[i]]$z[tempIndex]
  Variance[[i]]$FiedlerVec <- Summaries[[i]]$FiedlerVec[tempIndex]
  Variance[[i]]$Flexibility <- Summaries[[i]]$slideFlexibility[tempIndex]
  Variance[[i]]$propDMN <- Summaries[[i]]$slidePropDMN[tempIndex]
  Variance[[i]]$varCoeff <- Summaries[[i]]$varCoeff[tempIndex]
  Variance[[i]]$Region <- ifelse(Variance[[i]]$tempY < 0, "PCC", "mPFC")
}

@@

``` {r Correlation vs community detection: plot, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 16. Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (7m-based) and the Fiedler vector. The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE, cache = TRUE}
corrplot(allHalfCombs, 
         #title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.6,
         cl.pos = "b",
         mar = c(0,0,3,0))
segments(0.5,0.5,0.5,40.5, lwd = 2)
segments(0.5,0.5,40.5,0.5, lwd = 2)
segments(0.5,40.5,40.5,40.5, lwd = 2)
segments(40.5,0.5,40.5,40.5, lwd = 2)
segments(0.5,20.5,40.5,20.5, lwd = 2)
segments(20.5,0.5,20.5,40.5, lwd = 2)

@@

>>>>

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
output:
  pdf_document: default
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

Next, we identified areas that were solely related to either literature. We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al. [-@Yeo2011]. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a area-wise chi-squared test of proportions on the number of permuted studies that had reported each area. This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.

@@

In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) [@Hubert1985] as the reference metric of agreement between two clusterings. The adjusted rand index estimates the rate at which every pair of nodes in partition A were equally assigned to the same/different parcels on partition B, over all possible changes (e.g. clustered together on A, but separately on B). The resulting ratio is compared to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions. Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme. Note that this metric is adjusted for chance cluster labelings, and thus heavily penalizes deviations.

@@

Before determining the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004]. Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model. Since modularity is agnostic to the desired number of clusters, it was capable of finding more than two communities in our datset. Thus, if both methods agreed in the number and topological organization of the current communities, it would add confidence to our results. We quantified the cross-method agreement with the adjusted rand index (ARI). ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g. clustered together in partition 1, but separately in 2), and has the benefit of being agnostic to labeling schemes [@Hubert1985]. Figure 3 shows the distribution of ARI values across subjects.

@@

``` {r Partition comparison: all 2 (Fig. 4), fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}

# par(mfrow = c(1,2))
# corrplot(RI_all_between,
#          is.corr = F, 
#          method = "color", 
#          tl.pos = "n", 
#          tl.col = "black", 
#          cl.lim = c(0,1),
#          cl.pos = "b",
#          cl.length = 3)
# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         cl.lim = c(0,1),
         cl.length = 3,
         addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,1,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         addgrid.col = "grey90",
         mar = c(1,1,2,0), 
         add = T)
segments(0.5,0.5,0.5,100.5, lwd = 2)
segments(0.5,0.5,100.5,0.5, lwd = 2)
segments(0.5,100.5,100.5,100.5, lwd = 2)
segments(100.5,0.5,100.5,100.5, lwd = 2)
mtext(expression(bold("Subject Partitions")), line = 3)
mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Partition comparison: halves (Fig. 5), fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1))
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
corrplot(RI_PCC_halves, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
corrplot(RI_PFC_halves, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

@@

# plot
ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_violin(show.legend = F, draw_quantiles = 0.5, trim = F, lwd = 0.7) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, NA) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

@@

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

@@

As before, we see higher agreement levels within subjects (with some exceptions). Note that the overall ARI has markedly diminished for mPFC, which is expected as the 15 minute sessions are too short to determine stable community patterns [@Gordon2017]. Nevertheless, we can still coarsely capture a subject's unique organizational pattern. Simple permutation comparisons confirmed this intuition for the all-ROI (p = `r Sess_overallComparison[[3]]$Pval`; Cohen's D `r round(Sess_overallComparison[[4]], digits = 2)`), PCC (p = `r Sess_PCCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PCCComparison[[4]], digits = 2)`), and mPFC (p = `r Sess_PFCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PFCComparison[[4]], digits = 2)`) divisions. In order to quantify the consistency and specificity of these partitions, we again applied the RI ratio index, but this time using the mean RI among all of a subject's sessions in the denominator. The following plot shows the results for PCC and mPFC separately.

@@

ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_violin(show.legend = F, draw_quantiles = 0.5, trim = F, lwd = 0.7) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, NA) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

@@

### *Stability per subject (sliding window)*

@@

## PLAYING WITH AR AND MA PROCESSES
# tempSC <- do.call(rbind, SC)
# tempSC <- SC_PFC
# tempSC$SubjID <- as.factor(tempSC$SubjID)
# test <- numeric()
# intercepts <- numeric()
# coefficients <- numeric()
# 
# for (i in seq(100)) {
#   temp <- arima(SC[[i]]$Index, c(1,0,0), method = "ML")
#   test <- c(test, temp$residuals)
#   intercepts[i] <- temp$coef[2]
#   coefficients[i] <- temp$coef[1] 
# }
# 
# tempSC$Res <- test
# 
# ggplot(data = tempSC, aes(Window, Res, group = SubjID, color = SubjID)) +
#   geom_line(show.legend = F, alpha = 0.5) +
#   theme_classic()
# 
# ggplot(data = tempSC, aes(Res, group = SubjID, color = SubjID)) +
#   geom_density(alpha = 0.5, show.legend = F) +
#   theme_classic()
# 
# 
# test <- aggregate(SC_PCC$Index, by = list(SC_PFC$SubjID), arima, order = c(10,0,0), method = "ML")
# intercepts <- numeric()
# coefficients <- numeric()
# for(i in seq(100)) {
#   intercepts[i] <- test$x[[i]]['intercept']
#   coefficients[i] <- test$x[[i]]['ar1']
# }
# 
# plot(intercepts)

# AND WITH MORE SIMILARITY MATRICES
# THE POINT HERE IS THAT I TOOK THE ARI SIMILARITY MATRIX OF ALL THE SLIDING WINDOWS PER SUBJECT AND AVERAGED ACROSS SUBJECTS
# THIS PRODUCES A MATRIX WHERE YOU CAN TELL THE AUTOCORRELATED NATURE OF THE DATA IF UNCLUSTERED, BUT OTHERWISE THERE ARE MARKED DAY CLUSTERS
# simMatrices <- list()
# nrun <- 1
# for (subj in SVals) {
#   nWins <- ncol(subj)
#   if (nWins != 37) {
#     print("Fewer than 37 windows...")
#   } else {
#     tempMat <- matrix(NA, nWins, nWins)
#     for (i in seq(nWins)) {
#       for(j in seq(nWins)) {
#         tempMat[i,j] <- arandi(subj[,i], subj[,j], adjust = T)
#       }
#     }
#     simMatrices[[nrun]] <- tempMat
#     nrun <- nrun + 1
#   }
# }
# 
# meanMatrices <- Reduce("+", simMatrices) / length(simMatrices)
# corrplot(meanMatrices, method = "color", is.corr = F, cl.lim = c(0,1))
```

@@

### Grab some of the other measures from the overall summary
for (i in seq(nSubj)) {
  tempIndex <- Summaries[[i]]$Vertex %in% Variance[[i]]$Vertex
  Variance[[i]]$SubjID <- rep(subjList[i], nrow(Variance[[i]]))
  Variance[[i]]$FiedlerVec <- Summaries[[i]]$FiedlerVec[tempIndex]
  Variance[[i]]$Flexibility <- Summaries[[i]]$slideFlexibility[tempIndex]
  Variance[[i]]$propDMN <- Summaries[[i]]$slidePropDMN[tempIndex]
  Variance[[i]]$varCoeff <- Summaries[[i]]$varCoeff[tempIndex]
  Variance[[i]]$Region <- ifelse(Variance[[i]]$tempY < 0, "PCC", "mPFC")
}

@@

``` {r Correlation vs community detection (Fig. 16), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 16. Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (7m-based) and the Fiedler vector. The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE, cache = TRUE}
corrplot(allHalfCombs, 
         #title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
         method = "color", 
         #tl.col = "black",
         #tl.cex = 0.6,
         addgrid.col = "grey90",
         tl.pos = "n",
         cl.pos = "r",
         cl.length = 3,
         mar = c(1,2,2,0))
segments(0.5,0.5,0.5,40.5, lwd = 2)
segments(0.5,0.5,40.5,0.5, lwd = 2)
segments(0.5,40.5,40.5,40.5, lwd = 2)
segments(40.5,0.5,40.5,40.5, lwd = 2)
segments(0.5,20.5,40.5,20.5, lwd = 2)
segments(20.5,0.5,20.5,40.5, lwd = 2)
mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), line = 3, at = par("usr")[1]+0.45*diff(par("usr")[1:2]))
mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), side = 2, line = 3)
mtext(expression(bold("Fiedler")), line = 1.5, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))
mtext(expression(bold("Correlation")), line = 1.5, at = par("usr")[1]+0.23*diff(par("usr")[1:2]))
mtext(expression(bold("Fiedler")), side = 2, line = 2, at = par("usr")[1]+0.25*diff(par("usr")[1:2]))
mtext(expression(bold("Correlation")), side = 2, line = 2, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))

@@

It might also be worth mentioning that previous work has established the shift in network types during rest through hidden Markov models (Vidaurre et al., 2016?). While this suggests that we should see fluctuations in affiliation, and not stability, Vidaurre's work establishes the dynamics of prevalent function among networks, and not their topologies. Our work focuses on the topographical arrangement of the DMN network, which can be active or not while maintaining its form. So, the two works are compatible. Note, I played a bit with AR and MA processes per subject to try to understand the autocorrelation in the sliding window. First, both acf/pacf and arima (order = n,0,n) R functions suggested that the data was better fit by AR. Moreover, ARs from 1 to 10 had neglegible differences, so I stuck with 1 results for simplicity. As expected the data is significantly autocorrelated, and when I checked plotted the residuals they were mostly within the 0.15 bound (normally distributed). Coefficients ranged from 0.6 to 1. So, there is clear rythmicity in the agreement between each window and the overall pattern. However, the intercepts from the ARn processes gave more or less the same estimates as the mean rand index over all the windows. This is mostly expected, as we saw that the standard deviation of the rand index was low across participants. I am currently interpreting this as a signal that there is clear periodicity that is otherwise harmless for our results: in the end, the agreement remains stable throughout the 4800 TRs.
